Body size patterns

### 2019-07-25 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
added CS fig

@@

ggplot(plotByRiver, aes(x)) +
  geom_line(aes(y = y, color = speciesGG), size = 1.5) +
  geom_ribbon(aes(ymin = lowerCI, ymax = upperCI, fill = speciesGG), alpha = 0.5, show.legend = FALSE) +
  scale_color_manual(values = c('grey30', 'grey70')) +
  scale_fill_manual(values = c('grey30', 'grey70')) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Species') +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face="plain")) +
  facet_wrap(~ riverGG)

>>>>

ggplot(cohortStrengthWide %>% filter(cohort >= 2002), aes(cohortStrengthScaledBKT, cohortStrengthScaledBNT, color=factor(cohort))) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)

@@

ggplot(plotByRiver, aes(x)) +
  geom_line(aes(y = y, color = speciesGG), size = 1.5) +
  geom_ribbon(aes(ymin = lowerCI, ymax = upperCI, fill = speciesGG), alpha = 0.5, show.legend = FALSE) +
  scale_color_manual(values = c('grey30', 'grey70')) +
  scale_fill_manual(values = c('grey30', 'grey70')) +
  labs(y = 'Effect on body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Species') +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face="plain")) +
  facet_wrap(~ riverGG)
